|

### 2019-12-31 inst/manuscript/candidaev_figures.Rmd
Make minute change to candidaev_figures.Rmd

test <- nta_binned %>% 
  mutate(bin = as.factor(bin))

test2 <- aov(Particle_count ~ Strain * bin, data = test)
summary(test2)

TukeyHSD(test2, which = "Strain")

@@

# construct figure 2c
nta_total$Strain <- factor(nta_total$Strain, 
                           levels = c("DAY286", "ATCC90028", 
                                      "ATCC10231", "Biofilm"))

>>>>

@@

# construct figure 1c
nta_total$Strain <- factor(nta_total$Strain, 
                           levels = c("DAY286", "ATCC90028", 
                                      "ATCC10231", "Biofilm"))
